Monte Carlo Bootstrap: current developments.

### 2019-05-05 draft.tex
commented all that could be commented

@@

@@

>>>>

\subsection{Determination of the external operator's dimension}
An interesting application of this method is determining the dimension of the
external operator. The main obstacle to overcome is due to the fact that the
action depends on this parameter very differently when compared to the exchanged
operators' dimensions. Also, the contribution of the identity operator, which
depends only on the external operator, exhibited a spurious runaway
behaviour that needed to be controlled.

The current working solution is to allow the MC to optimize this parameter but
to impose artificial bounds on the values it can probe, thus creating bins for
the external dimension.

@@

\subsection{Parallel implementation}
Given the extensive computational cost of evaluating the conformal blocks and
calculating the minors thereof we devised a parallel algorithm that splits the
set $\{N_z\}$ into subsets of equal cardinality and assigns the task of
evaluating the elements of the matrix corresponding to each subset to a
different kernel. Each kernel then calculates the respective minors and returns
to the main process their contribution to the action. This entails a
considerable speedup when working with 20 processors and $O(1000)$ points.

@@

Alternatively, the multipoint approach can determine the dimensions for the 5
lowest-lying operators with a relative error of $O(10^{-3})$, but it still needs
to be refined in order to perform properly at higher $l$.

We have also results which agree with Maldacena's theorem %cite Maldacena
In these simulations we fix the dimension of a higher spin operator ($l=4$ or
$l=6$) to the value that saturates the unitarity bound, i.e. we forse them to be
conserved currents. In this case, the multipoint logdet MC shows very clearly
that all the other operators, including the external operator, find the minimum
corresponding to the free theory.
